Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
suceed to put n=x

## try with CV
 cv_by_site_df_label <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
   mutate(label = as.factor(paste0(sitename,'\nN = ',n))) %>%   select(-n) %>% 
 nest(-sitename, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))

cv_by_site_df_unnest_label <-   
cv_by_site_df_label %>% 
  unnest(cv_by_site, label)

cv_plot_site_label <- cv_by_site_df_unnest_label %>% 
  select(-data)

library(tidyr)
cv_plot_site %>% 
pivot_longer(cols = -sitename, names_to = "group") %>% 
ggplot(aes(x = sitename, y = value, fill = as.factor(group))) + 
geom_bar(stat="identity", position=position_dodge())

>>>>

## CV with site (n=X)
 cv_by_site_df_label <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
   mutate(label = as.factor(paste0(sitename,'\nN = ',n))) %>%   select(-n) %>% 
 nest(-sitename, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))

cv_by_site_df_unnest_label <-   
cv_by_site_df_label %>% 
  unnest(cv_by_site)

cv_plot_site_label <- cv_by_site_df_unnest_label %>% 
  select(-data) %>%

library(tidyr)
p<- cv_plot_site_label %>% 
pivot_longer(cols = -c(sitename,label), names_to = "group") %>% 
ggplot(aes(label, value, fill = as.factor(group))) + 
geom_bar(stat="identity", position=position_dodge())

p + labs(x= "Site", fill = "Attributes")
```
